---
title: Generate Reproducible & Live HTML and PDF Conference Posters Using RMarkdown
poster_height: "46in"
poster_width:  "33in"
font_family: 'Cabin'
author:
  - name: Hem Nalini Morzaria-Luna
    affil: 1
    orcid: '0000-0002-1099-3857'
  - name: Stevie Walker
    affil: 2
  - name: Isaac C. Kaplan
    affil: 3
  - name: Chris Harvey
    affil: 3  
affiliation:
  - num: 1
    address: Long Live the Kings, 1326 5th Ave Suite 450, Seattle, Washington, United States. 
  - num: 2
    address: Boston College, Department of Earth & Environmental Sciences, 140 Commonwealth Ave, Chestnut Hill, Massachusetts, United States.
  - num: 3 
    address: Northwest Fisheries Science Center, Conservation Biology Division, 2725 Montlake Blvd East, Seattle, Washington, United States.
primary_colour: "#ade8f4"
secondary_colour: "#219ebc"
accent_colour: "#023047"
main_findings: "Warming impacts on salmon and herring have widespread ecosystem impacts"
column_numbers: 3
logoright_name: https://user-images.githubusercontent.com/11339490/230630283-502c610d-4837-4a71-a8bc-c7459fa3a623.png
logoleft_name: https://user-images.githubusercontent.com/11339490/221080115-55142753-1e09-4d8f-a0b4-df314d9dfd19.jpg
output: 
  posterdown::posterdown_betterport:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Climate change effects in the marine system of Puget Sound

We used an end-to-end deterministic simulation model to link the physiological effects of warming oceanography to ecosystem-level changes, and investigated temperature sensitivity. 


# Response to warming
In Puget Sound, an urban estuary in the Pacific Northwest, USA, climate change will reshape the ecosystem through bottom-up processes, affecting the abundance of groups at the base of the food web (i.e. phytoplankton and marine plants) and through top-down processes.

## Objective

Link scenarios of warming oceanography to Atlantis simulations that test to what extent ‘speeding up’ ecosystem-wide anabolic processes (e.g., gains due to higher growth rates) will be balanced by ‘speeding up’ catabolic processes (e.g., losses due to declines in assimilation rates or increases in predation mortality).

# Methods

Atlantis is an end-to-end ecosystem modeling approach that represents all trophic levels from bacteria to apex predators and humans. It integrates physical, chemical, ecological, and fisheries dynamics in a three-dimensional, spatially-explicit domain that uses an irregular polygon structure to represent important bioregional features. 

We used the climate change anomalies of future Sea Surface temperature and salinity from CMIP6 projections downscaled for Puget Sound by Walker et al. (Walker et al. 2022) to force Atlantis, we also tested temperature sensitivity parametrized for Chinook and coho salmon and Pacific Herring, and compared with a base scenario.

We used a Kitchell response curve (courtesy A. Rovellini)

# Results

Chinook and Coho survival
Total system biomass
Biomass of phytoplankton

```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

Or with figures: Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}
plot(mtcars[1:2])
```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
data <- iris

plot(x = data$Sepal.Length, 
     y = data$Sepal.Width, 
     col = data$Species,
     pch = 19, 
     xlab = "Sepal Length (cm)",
     ylab = "Sepal Width (cm)")

```

# Next Steps

 We used a single-model ensemble approach, where multiple simulations are conducted with the same model, for a given scenario, while parameter values are varied between simulations (Gal et al. 2014). The model ensembles allows us to characterize parameter uncertainty (Payne et al. 2015); we developed eight different model ensemble members where invertebrate growth rates and fish and mammal density dependence vary within plausible ranges. We did not consider every parameter combination, but rather selected a subset that defines a ‘bounding box’ of possible parameter combinations that approximate the lower and upper bounds of observed system productivity (Fulton et al. 2014).
 
# Conclusion

Further research is needed on how to adequately implement physiological responses to ocean warming that can help understand potential future changes under climate change. 

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# More information

Walker et al. 2022. Future temperature and salinity in Puget Sound  

Morzaria-Luna et al. 2022 
